A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
Worked on conclusion

\subsection{Effect of data-intensive applications}
In our experiments, Incrementation, Histogram (NumPy) and Histogram for Spark have
low compute time while BIDS App example and Histogram for Dask have significantly
longer compute time. When adding additional workers, we observe that data-intensive
applications scale poorly while compute-intensive applications scale almost linearly
This is due to the limitation from the NFS, as mentioned above.

@@

>>>>

\subsection{Effect of data-intensive applications}
In our experiments, Incrementation, Histogram (NumPy) and Histogram for Spark have
low compute time while BIDS App example and Histogram for Dask have significantly
longer compute time. When adding additional workers, we observe that the highly
data-intensive applications scale poorly while compute-intensive applications scale
almost linearly This is due to the limitation from the NFS, as mentioned above.

@@

\section{Conclusion}
We presented a comparison of two Big Data engines: Spark and Dask. We studied the
engines on three data-intensive neuroimaging applications. Our results show no
substantial difference between the engines. Moreover, the majority of the execution
time was spent on data transfer and overhead. We also observed a possible correlation
between IO and overhead time: an higher overhead is compensated by a lower IO time and
a low overhead is compensated by an high IO time. This would be due to concurrent IO
tasks saturating the bandwidth. We suggest that current schedulers policies would benefit
from knowing the task types, either IO or compute, it is processing concurrently.
